\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.3in,right=0.4 in,bottom=0.3in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Jaman Uddin} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+880 167 385-0025 \\ Uttara, Dhaka, Bangladesh} 
\address{\href{mailto:zamaan.md19@gmail.com}{zamaan.md19@gmail.com} \\ \href{https://www.linkedin.com/in/rootprogrammer/}{linkedin.com/in/rootprogrammer} \\ \href{https://github.com/RootProgrammer}{github.com/RootProgrammer}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	SUMMARY
%----------------------------------------------------------------------------------------

\begin{rSection}{PROFESSIONAL SUMMARY}

{Seasoned Software Engineer with a robust five-year tenure at imranslab, excelling in Python and Django with an emphasis on AI/ML integration. Renowned for leading complex projects to fruition and catalyzing innovation. Mastery in blending Agile practices with engineering rigor to elevate application performance. Committed to continuous growth, with deep expertise in Object-Oriented Programming and complex data structures, poised to make significant advancements in Software Engineering.}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

%{\bf Master of Computer Science}, Stanford University \hfill {Expected 2020}\\
%Relevant Coursework: A, B, C, and D.

{\bf B.Sc.(Engg.) in Computer Science and Engineering (CSE)}, Asian University of Bangladesh \hfill {2018 - 2022}
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHNICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\renewcommand{\arraystretch}{1.5} % Adjusts the row height, 1.5 is a reference value
\begin{tabular}{@{} >{\bfseries}l 
  @{\hspace{6ex}} >{\raggedright\arraybackslash}p{12cm}}
Software Development & Python, Flutter (Beginner), Go (Beginner), YAML, Django, XML, JSON, RESTful Services, JavaScript, jQuery, Node.js, ReactJS\\

Technology Ecosystems & Django Rest API, FastAPI, RDBMS (Postgres, MongoDB, MySQL), REST, gRPC, Google Cloud Platform (GCP)\\

Quality Assurance \& DevOps & Selenium, Splinter, Postman, Docker, Terraform, CircleCI\\
%  Unit Testing, System Testing, Load Testing\\

Development Tools \& Methodologies & Git, GitHub, Jupyter Notebook, JIRA, Confluence, Sprints, Stand-Ups, Retrospectives\\

Collaboration \& Operating Systems &  Slack, Microsoft Teams, Windows, Debian, Ubuntu\\
\end{tabular}\\
\end{rSection}

\begin{rSection}{WORK HISTORY}

\textbf{Software Engineer} \hfill Feb 2019 - Present\\
imranslab \hfill \textit{Montréal, QC}
 \begin{itemize}
    \itemsep -3pt {} 
    \item Led the creation and ongoing refinement of a Job Finder platform and a Trading Predictor tool, utilizing Python and Django for core development.
    \item Initiated and implemented the integration of a Django Rest API with an Inventory Management System, ensuring smooth operation with a Flutter-based interface.
    \item Managed the modernization of an outdated codebase to a contemporary, object-oriented Django framework, employing GitHub for version control and Google Cloud Platform for hosting.
    \item Oversaw various projects, emphasizing teamwork and high-quality output, consistently achieving high standards of code performance and functionality.

 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\begin{itemize}
    \item \textbf{AI-Enhanced Job Finder (LinkedIn):} {Engineered AI algorithms to optimize resume evaluations, complemented by a sophisticated data management system for improved efficiency.}
    \item \textbf{Trading Analysis Platform:} {Overhauled and modularized a trading application using Django, integrating CI/CD practices for enhanced performance and agility.}
    \item \textbf{Inventory Management System:} {Spearheaded the development of a scalable inventory system, merging Django Rest API with Flutter for seamless operation and data accuracy.} 
\end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{Distinctive Milestones \& Passions} 
\begin{itemize} 
    \item \textbf{Achievements:} {Participated in ICPC Regional 2019, Google Kick Start 2021, showcasing strong problem-solving skills and a competitive mindset.}
    \item \textbf{Interests:} {Cutting-Edge Technology, Artificial Intelligence, Teaching, Watching Movies.}
\end{itemize}


\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{STRATEGIC COMMUNICATION \& LEADERSHIP EXCELLENCE} 
\begin{itemize}
    \item Proficient in Confluence for end-to-end project documentation, from initial requirements to post-deployment analysis, showcasing strong written communication.
    \item Ignited team success and innovation with dynamic leadership, merging visionary strategy and robust collaboration to steer projects to new heights, fostering an environment where creativity and collective problem-solving thrive.
\end{itemize}


\end{rSection}


\end{document}
